Nuclear Energy: Kahan scale and Economic Political value scale

### 2024-01-15 Paper1.Rmd
commiting after a long time. oh god

---
title: "Nuclear Energy: Kahan scale and Economic Political value scale"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    keep_tex: yes
  header-includes:
  - \usepackage{dcolumn}
  - \usepackage{array}
  - "\\usepackage{placeins}"
  keep_md: yes
---
```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
  knitr::opts_chunk$set(warning = FALSE, message = FALSE)

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(lavaan))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(psych)) 
```

@@

# code likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_I","K_H","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE", "DEV", "PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
               . == "Somewhat disagree" ~ 2,
               . == "Neither agree nor disagree" ~3,
               . == "Somewhat agree" ~ 4,
               . == "Strongly agree" ~ 5))) %>%

# reverse code for likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_S","K_E"))), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                               . == "Somewhat disagree" ~ 4,
                                                               . == "Neither agree nor disagree" ~3,
                                                               . == "Somewhat agree" ~ 2,
                                                               . == "Strongly agree" ~ 1))) %>%

# code eco-pol scale variables into numbers
mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG), funs(case_when(. == "Strongly disagree" ~ 1, 
                        . == "Somewhat disagree" ~ 2,
                        . == "Neither agree nor disagree" ~3,
                        . == "Somewhat agree" ~ 4,
                        . == "Strongly agree" ~ 5))) %>%

# reverse code eco-pol scale variables into numbers 
 mutate_at(vars(DECISIONCEN, INDUSTRYSMALL, ECONOMYLOCAL, ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                                                                         . == "Somewhat disagree" ~ 4,
                                                                                                         . == "Neither agree nor disagree" ~3,
                                                                                                         . == "Somewhat agree" ~ 2,
                                                                                                         . == "Strongly agree" ~ 1))) %>%
  mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
  mutate_all(~ifelse(. == "West bengal", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "WEST BENGAL", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "Up", "Uttar Pradesh", .))%>%
  mutate_all(~ifelse(. == "Tamilnadu", "Tamil Nadu", .))%>%
  mutate_all(~ifelse(. == "UP", "Uttar Pradesh", .))

@@

# H1: Nuclear Energy will be seen as riskier than other energy technologies in India.

## Likert Responses (n= 2160)
The percentages are rounded off to whole numbers.

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
# Q1: how much is the awareness of energy technologies in India ? How does it relate to state specific data ? 
# summary of NA results from the combined sample of 2000 responses (simple percentage bar graphs)
# part 1- how much is the awareness of energy technologies in India -

#plotting perceived risk from different technologies including rather not say don't know
colorsequence<- c("#8C4646","#D9695F","#F2A679","#F2D091","#5D8C7B","#808080")

#following is the data frame for making the barplot 
df_barplot <- uncodedjoineddf %>%
  dplyr::select(starts_with("RISKY"))%>%
  gather(Technology, Perceived_Risk, Risky_Hydro:Risky_INDLPG, factor_key = TRUE)%>%
  separate(Technology, c("Risky", "Technology"), extra = "merge", fill = "left")%>%
  dplyr::select(-Risky) %>% 
  group_by(Technology, Perceived_Risk) %>%
  dplyr::summarise(n=n())

#following data frame gives us percentage for each response 
df_barplot_percent<- df_barplot%>%
  group_by(Technology) %>%
  mutate(Percentage = round(n/sum(n)*100, 0)) %>%
  ungroup()

#plotting perceived benefit from different technologies including rather not say don't know

df_barplotben <- uncodedjoineddf %>%
  dplyr::select(starts_with("Ben"))%>%
  gather(Technology, Perceived_Benefit, Ben_Hydro:Ben_INDKerosene, factor_key = TRUE)%>%
  separate(Technology, c("Ben", "Technology"), extra = "merge", fill = "left")%>%
  dplyr::select(-Ben) %>% 
  group_by(Technology, Perceived_Benefit) %>%
  dplyr::summarise(n=n())

df_barplotben_percent<- df_barplotben%>%
  group_by(Technology) %>%
  mutate(Percentage = round(n/sum(n)*100, 0)) %>%
  ungroup()

#bar plot for likert responses perceived risk - centrally owned technologies 
df_barplot %>% ggplot(aes(fill= fct_rev(factor(Perceived_Risk, levels=c("Extremely risky", "Very risky","Moderately risky","Slightly risky","Not at all risky","Rather not say/Don't know"))), y=n , x=Technology)) + 
  geom_bar(position="fill",stat="identity")+
  geom_text(data = df_barplot_percent, aes(label=paste0(Percentage, "%"), y=n), position = position_fill(vjust=0.5), size=3) +
  scale_x_discrete(limits = c("Solar", "Wind" ,"Hydro", "Oil", "Coal","Gas", "Nuclear"))+
  scale_fill_manual("legend", values = c("Extremely risky" = "#8C4646", "Very risky" = "#D9695F", "Moderately risky" = "#F2A679", "Slightly risky" = "#F2D091","Not at all risky" = "#5D8C7B", "Rather not say/Don't know" = "grey94"))+
  labs( y = "Perceived Risk", x ="Centrally Managed Energy Technologies")+
  theme_classic()

#perceived benefit centrally owned technologies

df_barplotben %>% ggplot(aes(fill= factor(Perceived_Benefit, levels=c("Rather not say/Don't know","Not at all beneficial","Slightly beneficial","Moderately beneficial","Very beneficial", "Extremely beneficial")), y=n , x=Technology)) + 
  geom_bar(position="fill",stat="identity")+
   geom_text(data = df_barplotben_percent, aes(label=paste0(Percentage, "%"), y=n), position = position_fill(vjust=0.5), size=3) +
  scale_fill_manual("legend", values = c("Rather not say/Don't know" = "grey94" ,"Not at all beneficial" = "orange","Slightly beneficial"="yellow" ,"Moderately beneficial" = "palegreen","Very beneficial"= "green3", "Extremely beneficial"= "green4"))+
  scale_x_discrete(limits = c("Solar", "Wind", "Hydro", "Oil", "Coal","Gas","Nuclear"))+
  labs( y = "Perceived Benefit", x ="Centrally Managed Energy Technologies")+
  theme_classic()

@@

@@

# Calculate the mean for each technology for Risky
risky_mean <- risky_df %>%
  group_by(Tech) %>%
  summarize(Mean_Value = mean(Value, na.rm = TRUE),
          sd = sd(Value, na.rm = TRUE),
          se = sd(Value, na.rm = TRUE) / sqrt(n()),
          .groups = "drop")

# Do the same for Ben technologies
ben_mean <- ben_df %>%
  group_by(Tech) %>%
  summarize(Mean_Value = mean(Value, na.rm = TRUE),
          sd = sd(Value, na.rm = TRUE),
          se = sd(Value, na.rm = TRUE) / sqrt(n()),
          .groups = "drop")

@@

@@

# Generate the Ben plot with flipped y-axis
ben_plot <- ggplot(ben_mean, aes(y = Tech, x = Mean_Value)) +
  geom_bar(stat = "identity", fill = "palegreen3") +
  geom_errorbar(aes(xmin = Mean_Value - se, xmax = Mean_Value + se), width = 0.2) +
  coord_cartesian(xlim = c(4, 1)) + 
  labs(title = "Perceived Benefit", x = "Mean Values") +
  #scale_x_reverse() +
  theme(  # remove y-axis labels
        axis.title.y = element_blank()) + # remove the "Tech" axis title
  geom_vline(data = subset(combined_mean, Category == "Beneficial"), 
             aes(xintercept = mean_risk), linetype="dotted", color = "black", size = 0.5)

# Generate the Risky plot
risky_plot <- ggplot(risky_mean, aes(y = Tech, x = Mean_Value)) +
  geom_bar(stat = "identity", fill = "firebrick2") +
  geom_errorbar(aes(xmin = Mean_Value - se, xmax = Mean_Value + se), width = 0.2) +
  coord_cartesian(xlim = c(1, 4)) + 
  labs(title = "Perceived Risk", x = "Mean Values") +
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank())+
  geom_vline(data = subset(combined_mean, Category == "Risky"), 
             aes(xintercept = mean_risk), linetype="dotted", color = "black", size = 0.5)
 # remove the "Tech" axis title

@@

## Boxplot for perceived benefit and perceived risk by technology

```{r, echo = FALSE, fig.width=16, fig.height=6}

#Box plot to see the distribution

# Loading the required libraries
library(tidyverse)
library(stringr)
library(gridExtra)

# Reshape the data to a long format
joineddf_subset_long <- joineddf_subset %>%
  pivot_longer(cols = everything(), 
               names_to = "variable",
               values_to = "value")

# Separate the data into two: one for "Risky_" variables and one for "Ben_" variables
risky_df <- joineddf_subset_long %>% 
  filter(str_detect(variable, "^Risky_")) %>%
  mutate(variable = str_remove(variable, "Risky_"))  # Remove the "Risky_" prefix

ben_df <- joineddf_subset_long %>% 
  filter(str_detect(variable, "^Ben_")) %>%
  mutate(variable = str_remove(variable, "Ben_"))  # Remove the "Ben_" prefix

# Remove NA values
risky_df <- risky_df %>% drop_na()
ben_df <- ben_df %>% drop_na()

# Create box plots
risky_plot <- ggplot(risky_df, aes(x = variable, y = value, fill = variable)) +
  geom_boxplot() +
  scale_fill_manual(values = rep("firebrick2", length(unique(risky_df$variable)))) +
  labs(x = "Energy Technologies", y = "Likert", fill = "Technologies") +
  ggtitle("Perceived risk") +
  theme_minimal()+
  theme(axis.text.y = element_text(size=20), 
        axis.text.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.title.x = element_text(size=20),
        title = element_text(size=20))+
  guides(fill = FALSE)

ben_plot <- ggplot(ben_df, aes(x = variable, y = value, fill = variable)) +
  geom_boxplot() +
  scale_fill_manual(values = rep("palegreen3", length(unique(ben_df$variable)))) +
  labs(x = "Energy Technologies", y = "Likert Responses", fill = "Technologies") +
  ggtitle("Perceived Benefit") +
  theme_minimal()+
  theme(axis.text.y = element_text(size=20), 
        axis.text.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.title.x = element_text(size=20),
        title = element_text(size=20))+
  guides(fill = FALSE)

# Put the two plots next to each other
grid.arrange(risky_plot, ben_plot, ncol = 2)

## Pairwise T-test: Mean perceived risk and mean perceived benefit (all energy technologies)

The red and green pairs indicate that there is a statistically significant difference between the means of the two groups. 
White and grey indicate - no differences between the means of the two groups.

```{r, echo = FALSE, fig.width=14, fig.height=6}
#Q2 :How are the perceptions of the risk of producing energy from nuclear fission different from that of other conventional sources of energy like coal or hydro power in India?
#H : Nuclear energy will be perceived as riskier than other sources of energy (coal or hydro) in India like in the west.
perceivedriskc <-joineddf %>% 
  dplyr::select("Risky_Solar", "Risky_Hydro", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil") %>%
  gather(key = "technology", value = "perceived_risk") %>% 
  mutate(technology = gsub("Risky_", "", technology)) %>%
  na.omit()

result_ttest <- pairwise.t.test(perceivedriskc$perceived_risk, perceivedriskc$technology, p.adjust.method = "BH")

# visualising the pairwaise t test results. the non significant pairs are grey

tidy_result_ttest <- broom::tidy(result_ttest)

heatmap1 <- ggplot(tidy_result_ttest, aes(x = group1, y = group2, fill = p.value)) + 
  geom_tile(color = "white") + 
  scale_fill_gradient2(low = "firebrick2", high = "white", midpoint = 0.025, 
                       limits = c(0, 0.05), space = "Lab", 
                       name = "P-value") + 
  theme_classic() + 
  labs(x = "", y = "") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
   theme(axis.text.y = element_text(size=20), 
        axis.text.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.title.x = element_text(size=20),
        title = element_text(size=20),
        legend.text = element_text(size=12))

#Question- Why there is significant difference statistically - if the medians are the same in the boxplot.
#Q3: How do perceptions of benefit from nuclear energy compare with other source of energy?

# H : benefits from all energy technologies will be similar 
# include regression, heat maps, bar graphs? - decide which ones are good to include

perceivedbenefitc <-joineddf %>% 
  dplyr::select("Ben_Solar", "Ben_Hydro", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil") %>%
  gather(key = "technology", value = "perceived_benefit") %>% 
  mutate(technology = gsub("Ben_", "", technology)) %>%
  na.omit()

result_ttestben <- pairwise.t.test(perceivedbenefitc$perceived_benefit, perceivedbenefitc$technology, p.adjust.method = "BH")

# visualising the pairwaise t test results. the non significant pairs are grey

tidy_resultbc <- broom::tidy(result_ttestben)

library(ggplot2)
heatmap2 <- ggplot(tidy_resultbc, aes(x = group1, y = group2, fill = p.value)) + 
  geom_tile(color = "white") + 
  scale_fill_gradient2(low = "palegreen3", high = "white", midpoint = 0.025, 
                       limits = c(0, 0.05), space = "Lab", 
                       name = "P-value") + 
  theme_classic() + 
  labs(x = "", y = "") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
   theme(axis.text.y = element_text(size=20), 
        axis.text.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.title.x = element_text(size=20),
        title = element_text(size=20),
        legend.text = element_text(size=12))

grid.arrange(heatmap1, heatmap2, ncol=2)

@@

alldemoslm1 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age , data = alldemos)
# Print model summary
#summary(alldemoslm1)
#plot(alldemoslm1)

@@

# 2) lm with all demographic variables
alldemoslm2<- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State, data = alldemos)
# Print model summary
#summary(alldemoslm2)
#plot(alldemoslm1)

@@

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(alldemoslm1_centered, alldemoslm2_centered, 
          title = "Results from 2 linear regression models",
          type = "latex"
)
cat("\\endgroup")

@@

alldemos_factor <-alldemos  %>%
  mutate_at(vars(Risky_Nuclear, Uppercaste, Male, Hindu, Urban, State), as.factor)

model= polr(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban +State , data = alldemos_factor, Hess = TRUE)
#summary(model)

model3 <- glm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban +State , data = alldemos_factor, family = binomial)
#summary(model3)

ci <- confint(model3)
#print(ci)

@@

@@

@@

@@

params1$Scale <- NA
params1$Scale[1:3] <- "Individualism"
params1$Scale[4:7] <- "Hierarchy-Egalitarianism"
params1 <- params1[, c("Scale", setdiff(names(params1), "Scale"))]
CFAkahan <- knitr::kable(params1, booktabs = TRUE, caption = "Confirmatory Factor Analysis(CFA) on Kahan et al(2007) scale adapted to India") %>%
  kable_styling(latex_options = c("striped","scale_down", "hold_position", "repeat_header"))%>%
  column_spec(column = 2, width = "4cm")

@@

#fa.parallel(ecopolall_cor)

# this suggests 2 factors if we go by FA or 8 by PCA. let's try both and see how they look conceptually

# running EFA using psych package

@@

@@

fascale_scores <- cbind(Kahan_Kscores, scores1) %>%
  rename(Pdevelop = MR1)%>%
  rename(Ndevelop = MR2) %>%
  dplyr::select(!starts_with(c("K_","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")))

@@

create_beautiful_radarchart <- function(data, color = "#00AFBB", 
                                        vlabels = colnames(data), vlcex = 0.7,
                                        caxislabels = NULL, title = NULL, ...){
  radarchart(
    data, axistype = 1,
    # Customize the polygon
    pcol = color, pfcol = scales::alpha(color, 0.5), plwd = 2, plty = 1,
    centerzero=FALSE,
    # Customize the grid
    cglcol = "grey", cglty = 1.5, cglwd = 1.5,
    # Customize the axis
    axislabcol = "black", 
     # Increase the axis label size
    cexc = 3,
    # Variable labels
    vlcex = vlcex, vlabels = vlabels, vlpos = 0.95,
    seg = 7, caxislabels = caxislabels, title = title, 
    # Increase title size
    cex.main = 2,
    ...
  )
}

# Reduce plot margin using par()
op <- par(mar = c(7, 3, 3, 3))
# Create the radar charts
create_beautiful_radarchart(
  data = radar2, caxislabels = c(-0.6,-0.4,-0.2, 0, 0.2, 0.4, 0.6, 0.8, 1),
  color = c("#00AFBB", "#F97D09"),
  vlcex = 1.1
)

@@

fa_table <- function(x, cut) {
  #get sorted loadings
  loadings <- fa.sort(x)$loadings %>% round(3)
  #supress loadings
  loadings[loadings > -cut & loadings < cut] <- ""
  #get additional info  
  add_info <- cbind(x$communalities, 
                    x$uniquenesses,
                    x$complexity) %>%
    # make it a data frame
    as.data.frame() %>%
    # column names
   rename("Communality" = V1,
           "Uniqueness" = V2,
           "Complexity" = V3) %>%
    #get the item names from the vector
    rownames_to_column("item")
  #build table
  loadings %>%
    unclass() %>%
    as.data.frame() %>%
    rownames_to_column("item") %>%
    left_join(add_info) %>%
    mutate(
      item = if_else(item %in% names(rename_map), rename_map[item], item),
      across(where(is.numeric), round, 3)
    )
}

>>>>

---
title: "Nuclear Energy: Kahan scale and Economic Political value scale"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    keep_tex: yes
  header-includes:
  - \usepackage{dcolumn}
  - \usepackage{array}
  - "\\usepackage{placeins}"
  keep_md: yes
---

# Abstract

Indian state regards nuclear energy as an important solution to rising energy needs and climate change issues. However, throughout India, nuclear power initiatives have faced opposition from people. Using survey data this study reveals that, similar to global trends, nuclear energy is perceived as highly risk in India as well. It is also perceived as the riskiest technology among all large-scale energy sources (like coal, solar, wind, oil gas, and hydro). Using risk perception theories and frameworks, this paper delves into the underlying factors influencing India's public perception of nuclear energy. While consistent demographic patterns, termed the "white male effect," influence risk perceptions in the US, demographic factors such as gender and caste have minimal influence on India's nuclear energy risk perceptions. Cultural paradigms like hierarchy versus egalitarianism and individualism versus communitarianism also show negligible impact. However, regional differences among states and economic and political values have significant impact on risk perceptions related to nuclear energy in the Indian context.

```{r load packages, warning = FALSE, message = FALSE, echo=FALSE}
  knitr::opts_chunk$set(warning = FALSE, message = FALSE)

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(lavaan))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(psych)) 
suppressPackageStartupMessages(library(foreign))
suppressPackageStartupMessages(library(MASS))
suppressPackageStartupMessages(library(Hmisc))
suppressPackageStartupMessages(library(reshape2))

@@

# code likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_S","K_E","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE","DEVNUCLEAR","PROSPER", "RELY"))), funs(case_when(. == "Strongly disagree" ~ 1, 
               . == "Somewhat disagree" ~ 2,
               . == "Neither agree nor disagree" ~3,
               . == "Somewhat agree" ~ 4,
               . == "Strongly agree" ~ 5))) %>%

# reverse code for likert scale for variables for Kahan scale into numbers
  mutate_at(vars(starts_with (c("K_H","K_I"))), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                               . == "Somewhat disagree" ~ 4,
                                                               . == "Neither agree nor disagree" ~3,
                                                               . == "Somewhat agree" ~ 2,
                                                               . == "Strongly agree" ~ 1))) %>%

# code eco-pol scale variables into numbers
mutate_at(vars(SYSTEMDEMO,SYSTEMRELIGION,SYSTEMTECHNO,SYSTEMTOTAL,WEALTHLIM,MECHANISATION,DECISIONDECEN,INDUSTRYSMALL,ECONOMYLOCAL,ENVOVERDEV,OWNERPUB, OWNERREG), funs(case_when(. == "Strongly disagree" ~ 1, 
                        . == "Somewhat disagree" ~ 2,
                        . == "Neither agree nor disagree" ~3,
                        . == "Somewhat agree" ~ 4,
                        . == "Strongly agree" ~ 5))) %>%

# reverse code eco-pol scale variables into numbers 
 mutate_at(vars(DECISIONCEN,INDUSTRYLARGE,ECONOMYGLOBAL,OWNERPVT,OWNERNOREG, DEVOVERENV), funs(case_when(. == "Strongly disagree" ~ 5, 
                                                                                                         . == "Somewhat disagree" ~ 4,
                                                                                                         . == "Neither agree nor disagree" ~3,
                                                                                                         . == "Somewhat agree" ~ 2,
                                                                                                         . == "Strongly agree" ~ 1))) %>%
  mutate_all(~ifelse(. == "Rather not say/ Don't know", "Rather not say/Don't know", .))%>%
  mutate_all(~ifelse(. == "West bengal", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "WEST BENGAL", "West Bengal", .))%>%
  mutate_all(~ifelse(. == "Up", "Uttar Pradesh", .))%>%
  mutate_all(~ifelse(. == "Tamilnadu", "Tamil Nadu", .))%>%
  mutate_all(~ifelse(. == "UP", "Uttar Pradesh", .))

@@

# Nuclear is seen as riskier than others -this paper explore this risk perception

@@

joineddf_subset_cor <- joineddf %>%
  dplyr::select(!starts_with(c("Ben_IND", "Risky_IND")))%>%
  dplyr::select(starts_with("Risky"), 
         starts_with("Ben"))%>%
  na.omit()

cor(joineddf_subset_cor)

@@

# Calculate the mean for each technology for Risky
risky_mean <- risky_df %>%
  group_by(Tech) %>%
  dplyr::summarize(Mean_Value = mean(Value, na.rm = TRUE),
          sd = sd(Value, na.rm = TRUE),
          se = sd(Value, na.rm = TRUE) / sqrt(n()),
          .groups = "drop")

# Do the same for Ben technologies
ben_mean <- ben_df %>%
  group_by(Tech) %>%
  dplyr::summarize(Mean_Value = mean(Value, na.rm = TRUE),
          sd = sd(Value, na.rm = TRUE),
          se = sd(Value, na.rm = TRUE) / sqrt(n()),
          .groups = "drop")

@@

# Split the data into Risky and Ben subsets
risky_data <- joineddf_subset_cor %>% dplyr::select(starts_with("Risky"))
ben_data <- joineddf_subset_cor %>% dplyr::select(starts_with("Ben"))

# Rename the columns
names(risky_data) <- gsub("^Risky_", "Perceived Risk (", names(risky_data))
names(risky_data) <- paste0(names(risky_data), ")")
names(ben_data) <- gsub("^Ben_", "Perceived Benefit (", names(ben_data))
names(ben_data) <- paste0(names(ben_data), ")")

# Compute the correlation between Risky and Ben variables
correlation_matrix <- cor(risky_data, ben_data)

correlation_df <- as.data.frame(correlation_matrix)

#kable_table <- kable(correlation_df, caption = "Correlation Table between Perceived Risk and Perceived Benefit Variables", format = "html", #digits = 2) %>%
  #kable_styling(full_width = F) %>%
  #column_spec(1, background = "white") %>%
  #add_header_above(c(" " = 1, "Perceived Benefits" = ncol(correlation_df)))#%>%
  #pack_rows("Perceived Risks", 1, nrow(correlation_df))

# Apply alternating background colors for columns
#for (i in seq(2, ncol(correlation_df), by = 2)) {
  #kable_table <- kable_table %>%

#row_spec(i, background = "#F0F0F0")
#}

# Print the kable table
#print(kable_table)
```

@@

# Generate the Ben plot with flipped y-axis
ben_plot <- ggplot(ben_mean, aes(y = Tech, x = Mean_Value)) +
  geom_bar(stat = "identity", fill = "palegreen3") +
  geom_errorbar(aes(xmin = Mean_Value - se, xmax = Mean_Value + se), width = 0.2) +
  coord_cartesian(xlim = c(5, 1)) + 
  labs(title = "Perceived Benefit", x = "Mean Values") +
  #scale_x_reverse() +
  theme(  # remove y-axis labels
        axis.title.y = element_blank()) + # remove the "Tech" axis title
  geom_vline(data = subset(combined_mean, Category == "Beneficial"), 
             aes(xintercept = mean_benefit), linetype="dotted", color = "black", size = 0.5)

# Generate the Risky plot
risky_plot <- ggplot(risky_mean, aes(y = Tech, x = Mean_Value)) +
  geom_bar(stat = "identity", fill = "firebrick2") +
  geom_errorbar(aes(xmin = Mean_Value - se, xmax = Mean_Value + se), width = 0.2) +
  coord_cartesian(xlim = c(1, 5)) + 
  labs(title = "Perceived Risk", x = "Mean Values") +
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank())+
  geom_vline(data = subset(combined_mean, Category == "Risky"), 
             aes(xintercept = mean_risk), linetype="dotted", color = "black", size = 0.5)
 # remove the "Tech" axis title

@@

@@

alldemoslm1 <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age , data = alldemos)
# Print model summary
summary(alldemoslm1)
#plot(alldemoslm1)

@@

# 2) lm with all demographic variables
alldemoslm2<- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban + age + State, data = alldemos)
# Print model summary
summary(alldemoslm2)
#plot(alldemoslm1)

@@

#cat("\\begingroup")
#cat("\\setlength{\\tabcolsep}{1pt}")
#cat("\\renewcommand{\\arraystretch}{0.7}")
#stargazer(alldemoslm1_centered, alldemoslm2_centered, 
          #title = "Results from 2 linear regression models",
          #type = "latex"
#)
#cat("\\endgroup")

@@

@@

##  kahan scale CFA, EFA and Alpha

@@

Kahan_scale <- codedmodule2 %>%
  dplyr::select(starts_with("K_"))

kahan.fa <- fa(Kahan_scale, nfactors = 2, rotate = "varimax")

print.psych(kahan.fa, sort = TRUE)

KahanHE<-Kahan_scale %>%
  dplyr::select(starts_with(c("K_H", "K_E")))

KahanHE_alpha<- psych::alpha(KahanHE, check.keys = TRUE) # alpha = 0.7

KahanSI<-Kahan_scale %>%
  dplyr::select(starts_with(c("K_S", "K_I")))

KahanSI_alpha<- psych::alpha(KahanSI, check.keys = TRUE) # alpha =0.52

KahanS<-Kahan_scale %>%
  dplyr::select(starts_with(c("K_S")))

KahanS_alpha<- psych::alpha(KahanS, check.keys = TRUE) # alpha = 0.72

KahanI<-Kahan_scale %>%
  dplyr::select(starts_with(c("K_I")))

KahanI_alpha<- psych::alpha(KahanI, check.keys = TRUE) # alpha = 0.31

@@

## Kahan scater plot from the CFA scores 
```{r, echo = FALSE}

Kahan_Kscores %>%
  ggplot(aes(KahanS, KahanH))+
  geom_count(aes(color = ..n.., size = ..n..))+
  guides(color = 'legend')+
  geom_hline(yintercept=0, colour="black", lwd=0.5)+
  geom_vline(xintercept=0, colour="black", lwd=0.5)+
  labs(x = "Individualism to Communitarianism", y = "Hierarchy to Egalitarianism")+
  ylim(-2,3)+
  xlim(-2,3)+
  theme_minimal() 
```

## alternative Kahan scores
```{r, echo=FALSE}

Kscalescores <- fascales %>%
  dplyr::select(!starts_with(("K_I")))%>%
  rowwise()%>%
  dplyr::mutate(Communitarianism_score = mean(c_across(K_SHARM:K_SPROTECT)))%>%
  dplyr::mutate(Egalitarianism_score = mean(c_across(K_HEQUAL:K_ERADEQ2)))%>%
  dplyr::select(!starts_with(c("K_I","K_S", "K_H", "K_E")))

# EDIT : Scatter plot of Kahan scale scores around the median scores on Individualism and Hierarchy scales

```{r dev = "jpg", echo=FALSE}

#scatter plot of Kahan scale scores around the median scores on Individualism and Hierarchy scales.

Kscalescores %>%
  ggplot(aes(Communitarianism_score,Egalitarianism_score))+
  geom_count(aes(color = ..n.., size = ..n..))+
  guides(color = 'legend')+
  geom_hline(yintercept=3, colour="black", lwd=1)+
  geom_vline(xintercept=3.5, colour="black", lwd=1)+
  labs(x = "Individualism to Communitarianism", y = "Hierarchy to Egalitarianism")+
  ylim(2,6)+
  xlim(2,6)+
  theme_minimal()

@@

params1$Scale <- NA
params1$Scale[1:3] <- "Communitarian"
params1$Scale[4:7] <- "Hierarchy-Egalitarianism"
params1 <- params1[, c("Scale", setdiff(names(params1), "Scale"))]
CFAkahan <- knitr::kable(params1, booktabs = TRUE, caption = "Confirmatory Factor Analysis(CFA) on Kahan et al(2007) scale adapted to India") %>%
  kable_styling(latex_options = c("striped","scale_down", "hold_position", "repeat_header"))%>%
  column_spec(column = 2, width = "4cm")

@@

#fa.parallel(ecopolall_cor)
# this suggests 2 factors if we go by FA or 8 by PCA. let's try both and see how they look conceptually 
# running EFA using psych package

@@

print.psych(ecopolall2.fa, sort = TRUE)

@@

fascale_scores <- cbind(Kahan_Kscores, scores1) %>%
  rename(Pdevelop = MR1)%>%
  rename(Ndevelop = MR2) #%>%
  #dplyr::select(!starts_with(c("K_","WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR")))

@@

create_beautiful_radarchart <- function(data, color = "#00AFBB", 
                                        vlabels = colnames(data), vlcex = 0.7,
                                        caxislabels = NULL, title = NULL, ...){
  radarchart(
    data, axistype = 1,
    # Customize the polygon
    pcol = color, pfcol = scales::alpha(color, 0.5), plwd = 2, plty = 1,
    centerzero=FALSE,
    # Customize the grid
    cglcol = "black", cglty = 1.5, cglwd = 1.5,
    # Customize the axis
    axislabcol = "black", 
     # Increase the axis label size
    cexc = 3,
    # Variable labels
    vlcex = vlcex, vlabels = vlabels, vlpos = 0.98,
    seg = 6, caxislabels = caxislabels, title = title, 
    # Increase title size
    cex.main = 2,
    ...
  )
}

# Reduce plot margin using par()
op <- par(mar = c(7, 3, 3, 3))
# Create the radar charts
create_beautiful_radarchart(
  data = radar2, caxislabels = c(-0.6,-0.4,-0.2, 0, 0.2, 0.4, 0.6, 0.8,1),
  color = c("#00AFBB", "#F97D09"),
  vlcex = 1.1
)

@@

fa_table <- function(x) {
  #get sorted loadings
  loadings <- fa.sort(x)$loadings %>% round(3)
  #supress loadings
  #loadings[loadings < cut] <- ""  # alternative loadings > -cut & loadings < cut
  #get additional info  
  add_info <- cbind(x$communalities, 
                    x$uniquenesses,
                    x$complexity) %>%
    # make it a data frame
    as.data.frame() %>%
    # column names
   rename("Communality" = V1,
           "Uniqueness" = V2,
           "Complexity" = V3) %>%
    #get the item names from the vector
    rownames_to_column("item")
  #build table
  loadings %>%
    unclass() %>%
    as.data.frame() %>%
    rownames_to_column("item") %>%
    left_join(add_info) %>%
    mutate(
      item = if_else(item %in% names(rename_map), rename_map[item], item),
      across(where(is.numeric), round, 3)
    )
}
